\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-05-01 jss/article.tex
corrections

\section[introduction]{Introduction}
%% Note: If there is markup in \(sub)section, then it has to be escape as above.
\pkg{Rgbp} uses Bayesian machinery to estimate a two-level model (a random-effects mixed model) and allows for a check of its frequentist properties via a repeated sampling procedure (which we call a ``method check"). It is found that even in small samples our procedure yields good frequency properties. Also, this package will be useful for Bayesians who want to see a non-informative reference point before and after constructing their full-Bayesian hierarchical model. For frequentists, it will provide confidence intervals of a random-effect mixed model with good repeated sampling properties.

@@

We also need a graphical summary that can give us valuable insight buried in pile of numbers and a function `\code{plot}' is exactly for this purpose.
\begin{CodeChunk}
\begin{CodeInput}
R> plot(p)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.25]{hospital1.png}
\end{center}
\end{figure}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> pcv <- coverage(p, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 5.5cm]{hospital2.png}
\end{center}
\end{figure}

@@

This summary also includes the result of logistic regression fit because we did not know prior means in advance. We had to estimate them via this logistic regression model. Let's look at the p-value of the indicator covariate (\code{beta1}). It shows that the two prior means distinguishing outfielders from other positions were significantly different, supporting your initial belief. The positive sign of $\hat{\beta}_{1}$ reflects on the first five players, outfielders, whose observed batting averages were higher than others.
\\
\begin{CodeChunk}
\begin{CodeInput}
R> plot(b)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.3]{baseball1.png}
\end{center}
\end{figure}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> bcv <- coverage(b, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 5.5cm]{baseball2.png}
\end{center}
\end{figure}

>>>>

\section[introduction]{Introduction}
%% Note: If there is markup in \(sub)section, then it has to be escape as above.
\pkg{Rgbp} uses Bayesian machinery to estimate a two-level model (a random-effects mixed model) and allows for a check of its frequentist properties via a repeated sampling procedure (which we call a ``method checking"). It is found that even in small samples our procedure yields good frequency properties. Also, this package will be useful for Bayesians who want to see a non-informative reference point before and after constructing their full-Bayesian hierarchical model. For frequentists, it will provide confidence intervals of a random-effect mixed model with good repeated sampling properties.

@@

We also need a graphical summary that can give us valuable insight buried in pile of numbers and a function `\code{plot}' is exactly for this purpose.
\begin{CodeChunk}
\begin{CodeInput}
R> plot(p)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.25]{hospital1.png}
\caption{Shrinkage plot and 95\% interval plot}
\end{center}
\end{figure}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> pcv <- coverage(p, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 5.5cm]{hospital2.png}
\caption{Coverage plot via method checking}
\end{center}
\end{figure}

@@

This summary also includes the result of logistic regression fit because we did not know prior means in advance. We had to estimate them via this logistic regression model. Let's look at the p-value of the indicator covariate (\code{beta1}). It shows that the two prior means distinguishing outfielders from other positions were significantly different, supporting your initial belief. The positive sign of $\hat{\beta}_{1}$ reflects on the first five players, outfielders, whose observed batting averages were higher than others.
\\
\begin{CodeChunk}
\begin{CodeInput}
R> plot(b)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.3]{baseball1.png}
\caption{Shrinkage plot and 95\% interval plot}
\end{center}
\end{figure}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> bcv <- coverage(b, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 5.5cm]{baseball2.png}
\caption{Coverage plot via method checking}
\end{center}
\end{figure}
